---
output:
  pdf_document: default
  html_document: default
---
Lecture3 practical exercises 
========================================================

#

In this practical we will use R to explore lyapunov exponents and doubling times of a simple class of one Dimensional map, tent map. The simplest tent map is symmetrical and is defined by 

\[ x_{i+1}  = \left\{ \begin{array}{ll} 2x_{i} & 0 < x_{i} \le 1/2  \\
    -2x_{i}+2 & 1/2 < x_{i} \le 1 \end{array} \right. \]

We can define a general tent map by
\[ x_{i+1}  = \left\{ \begin{array}{ll} \frac{x_{i}}{A} & 0 < x_{i} \le A  \\
    -\frac{x_{i}}{1-A}+\frac{A}{1-A}+1 & A < x_{i} \le 1 \end{array} \right. \]
The functions and script files that you need can be found in the shared folder: tentmap.m, lyapunov.m, doublingtime.m, Qplingtime.m.

```{r}
setwd("/Users/hailiangdu/HDU/Teaching/NanJing_SummerSchool/workshops")
source('doublingtime.R')
source('tentmap.R')
source('lyapunov.R')
source('Qplingtime.R')
```

## 1. Find the finite time (one step) Lyapunov exponent, $\lambda$, of the tent map for the parameter values $A = 0:01,...,0.99$. Plot $\lambda$ against $A$.


```{r}

```

## 2. For the same values of $A$, find the mean doubling time of the tent map. Plot $\tau_2$ against $A$.

```{r}


```

## 3. Do the estimates of the Lyapunov exponent depend on $\epsilon$, the initial separation?

Large values of epsilon can give you poor estimates.  Remember that Lyapunov exponents are defined as the limit as epsilon tends to zero.

## 4. Do the estimates of the Doubling time depend on $\epsilon$, the initial separation?

Yes, large values of epsilon may lead to the gradient of the perturbed initial condition differs from that of the initial condition. 

## 5. Find the analytical Lyapunov exponent as a function of A (Hint: system values are uniformly distributed over (0, 1)). How does this compare with the values found in part 1.?

The analytical lyapunov exponent is given by $A*\log_2(1/A)+(1-A)*\log_2(1/(1-A))$.  This is because there is a probability of $A$ that the gradient is $1/A$ and a probability of $1-A$ that the gradient is $1/(1-A)$.

```{r}

```

## 6. For the same values of A as you used in parts 1 and 2, compute the 4-pling time $\tau_4$ (the average time it takes for an initial error to grow to 4 times its initial value) of the tent map. Do the same for $\tau_8$ and $\tau_16$. Is $\tau_{2k}$ = $2\tau_k$?

```{r}

```