---
output:
  pdf_document: default
  html_document: default
---
Lecture2 practical exercises 
========================================================

#

Following the Lecture1 practical exercises, we continue working on Logistic Map to explore some general properties about nonlinear chaotic systems. 

The mathematical form of the Logistic map is 
$$
x_{i+1}=ax_i(1-x_i).
$$ 

##

We first investigate what happens to the initial condition under the action of the Logistic map, i.e. after a 'large' number of iterations, and how it differs with different parameter values. You may use the available code from last practical (and any other code that you find or write yourself).

```{r}
setwd("/Users/hailiangdu/HDU/Teaching/NanJing_SummerSchool/workshops")
source('logistic.R')
```

1. $x_{0} < 0$ or $x_{0} > 1$  and $ 0 < a < 4$

```{r}
```

2. $0 < x_{0} < 1$ and $a < 0$ or $a > 4$
3. $0 < x_{0} < 1$ and $a < 0$
4. $0 < x_{0} < 1$ and $0 < a < 1 $
5. $0 < x_{0} < 1$ and $1 < a < 3 $
6. $0 < x_{0} < 1$ and $a = 1+\sqrt(6)$
7. $0 < x_{0} < 1$ and $a = 3.5685$
8. $0 < x_{0} < 1$ and $a = 4$


##

Now let's investigate whether Logistic map has the property of sensitive dependence on initial condition.

1. consider $0.1 < x_{0} < 0.9$ and $x_{0} +\epsilon, \epsilon < 0.1$, after how many iterations are the two resulting states seperated by more than 0.5?
2. consider $0.1 < x_{0} < 0.9$ and $x_{0} +\epsilon, \epsilon < 0.01$, after how many iterations are the two resulting states seperated by more than 0.5?
3. consider $0.1 < x_{0} < 0.9$ and $x_{0} +\epsilon, \epsilon < 0.001$, after how many iterations are the two resulting states seperated by more than 0.5?
4. consider $0.1 < x_{0} < 0.9$ and $x_{0} +\epsilon, \epsilon < 0.0001$, after how many iterations are the two resulting states seperated by more than 0.5?
5. consider $0.1 < x_{0} < 0.9$ and $x_{0} +\epsilon, \epsilon < 0.00001$, after how many iterations are the two resulting states seperated by more than 0.5?
6. consider $0.1 < x_{0} < 0.9$ and $x_{0} +\epsilon, \epsilon < 0.000001$, after how many iterations are the two resulting states seperated by
  more than 0.5?

**consider $0 < x_{0} < 1$ and $a=4$,\ will the final state be equal to $x_{0}$ after a number of iterations?

##

Advanced work: 

i) Generate a long time series of points from the logistic map initialising from some $x_0\in[0, 1]$ and draw the parameter a from $U(2.4, 4)$. After
1024 points, continue but with a new value of $a$ drawn from $U(2.4, 4)$. Repeat, drawing new values of a every 1024 points. Once you have reached a certain predetermined number of different parameter values (for example 128 or 256), stop. Make a scatter plot with the parameter value
on the x axis and the system values on the y axis.

```{r}

```

ii) Repeat task i) but this time change the parameter value every 2048 steps. Make a new scatter plot but with only the final 1024 points for each parameter value (ignoring the first 1024).

```{r}

```

